% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author)
%       http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com>
%       http://www.davidgrant.ca
% (c) 2007 Todd C. Miller <Todd.Miller@courtesan.com>
%       http://www.courtesan.com/todd
% (c) 2009-2010 George R. Louthan IV <georgerlouth@nthefourth.com>
%       http://georgerloutha.nthefourth.com
%
% This work is licensed under the Creative Commons Attribution-Noncommercial-
% Share Alike 2.5 License. To view a copy of this license, visit
% http://creativecommons.org/licenses/by-nc-sa/2.5/ or send a letter to:
%
% Creative Commons
% 543 Howard Street
% 5th Floor
% San Francisco, CA 94105

\documentclass[letterpaper,11pt]{article}

% Margin setup

\setlength{\voffset}{0.1in}
\setlength{\paperwidth}{8.5in}
\setlength{\paperheight}{11in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\textheight}{11in}
\setlength{\textheight}{9.5in}
\setlength{\topmargin}{-0.25in}
\setlength{\textwidth}{7in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\evensidemargin}{-0.25in}

% Style setup

\usepackage{tabularx}
\usepackage{array}
\usepackage{color}
\usepackage{calc}
\definecolor{mygrey}{gray}{0.85}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\pagestyle{empty}


% Custom commands

% Resume item: corrects spacing for itemized entries (includes \item)
\newcommand{\resitem}[1]{\item \parbox[t]{4.6in}{#1} \vspace{-2pt}}

% Resume item description (not ready yet.) Like \resitem but in a
% description environment.
\newcommand{\resitemd}[2][]{\item[#1] #2 \vspace{-2pt}}

% Resume heading. Heading inside a shaded box.
\newcommand{\resheading}[1]{{\large \colorbox{mygrey}{\begin{minipage}
    {\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}

% Resume entry (used for subheading)
\newcommand{\resentry}[3][0pt]{
    \begin{tabular*}{0.9\textwidth}[t]{@{\hspace{#1}}p{5.0in-#1}@{\extracolsep{\fill}}p{0.75in}}
    %\begin{tabular}[t]{p{5.0in}@{\hfill}p{0.75in}}
        #2 & #3
        \tabularnewline
    \end{tabular*} %\vspace{-6pt}
}

% Resume subheading
\newcommand{\ressubheading}[4]{
    \resentry{\textbf{#1} \newline #3}{#2 \newline #4}    
}

% Resume subheading with extra information
\newcommand{\ressubheadingextra}[5]{
    \resentry{\textbf{#1} \newline #3 \newline #5}{#2 \newline #4}
}

% Specific entry types:

% School:
% School, Location, Description, Degrees
\newcommand{\resschool}[3]{
    \resentry{\textbf{#1} \newline #3}{#2}
}

\newcommand{\resschoolextra}[4]{
    \resentry{\textbf{#1} \newline #3 \newline #4}{#2}
}

% Degree:
% Degree, Major, Date, Description
\newcommand{\resdegree}[3]{
    \resentry[10pt]{
\setlength{\parskip}{1ex plus 0.5ex minus 0.2ex} #1 #2}{#3}
}

\newcommand{\resdegreeextra}[4]{
    \resentry[10pt]{
\setlength{\parskip}{1ex plus 0.5ex minus 0.2ex} #1 #2 \newline #4}{#3}
}

% Combined school and degree (plus other) entry:
% University, Degree, Major, Date, Location, Other
\newcommand{\reseducation}[6]{
    \ressubheadingextra{#1}{#5}{#2 #3}{#4}{#6}
}

% Work experience:
% Employer, Location, Description, Jobs
\newcommand{\resemployer}[4]{
    \resentry{\textbf{#1} \newline #3 \newline #4}{#2}
}

% Work experience:
% Title, Start Date, End Date, Description
\newcommand{\resjob}[4]{
    \resentry[10pt]{
\setlength{\parskip}{1ex plus 0.5ex minus 0.2ex} \textbf{#1} \newline #4}{#2 - \newline #3}
}

\begin{document}

% Heading and name/contact info table
\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
\textbf{\Large George R. Louthan IV}  & 918.289.2458\\
20 E Archer \#604 &  georgerlouth@nthefourth.com \\
Tulsa, OK 74103 & http://georgerloutha.nthefourth.com \\
\end{tabular*}
\\

\vspace{0.1in}

\resheading{Education}
\begin{itemize}
\item
        \resschool{University of Tulsa}{Tulsa, OK}{
            \resdegreeextra{M.S.}{Computer Science}{May 2011}{(expected)}
            \resdegree{B.S.}{Computer Science}{May 2009}
            \resdegree{B.S.}{Mathematics}{May 2009}
        }
        
%        \resdegree{University of Tulsa}{M.S.}{Computer Science}{May 2011}
%        {Tulsa, OK}{Thesis: Formal Modeling of Hybrid Systems}
%\item
%        \resdegree{University of Tulsa}{B.S.}{Computer Science}
%        {May 2009}{Tulsa, OK}{B.S. Mathematics}
\end{itemize}

%%%%%%%%%%%%%%%%%
% Certs: comment for short form
\resheading{Certifications}
\begin{itemize}
\item
	\ressubheading{CNSS 4011-4016}{Tulsa, OK}{Issued by the University of Tulsa. National Information Assurance Training Standards:}{2006 - 2011}
        \begin{description}
		\item[4011] for Information Systems Security Professionals
		\item[4012] for Senior Systems Managers
		\item[4013] for System Administrators
		\item[4014] for Information Systems Security Officers (Expected 2011)
		\item[4015] for Systems Certifiers
		\item[4016] for Risk Analysts
        \end{description}
\end{itemize}

% End certs


\resheading{Employment History}
\begin{itemize}
\item
\resemployer{University of Tulsa}{Tulsa, OK}
{Small research university with a prestigious information security program and
extensive research operations under its Institute for Information Security, an
NSA/CSS Center of Excellence in information assurance.}
{
    \resjob{Graduate Research Assistant}{May 2009}{Present}{
        Part of TU's Institute for Information Security's security engineering
        research initiative. Serving as the student lead for a formal methods
        research project. Also collaborating with researchers in cyber security
        training, information visualization, and critical infrastructure
        protection initiatives. Peer-reviewed publications in cyber security
        education, network intelligence, and secure collaboration.
        
        Also led the development and deployment of the Institute's IT infrastructure
        and supervising its upkeep (approximately 40 workstations and 5 servers).
    }
    \resjob{Graduate Teaching Assistant}{Jan 2010}{May 2010}{
        Taught a sophomore-level programming lab in the Java language. Developed
        supplementary course materials on code style, algorithms, documentation,
        and best practices.
    }
    \resjob{Undergraduate Research Scientist}{May 2006}{May 2009}{
        Undergraduate researcher in the Enterprise Security Group. Worked in
        enterprise security management, threat modeling, network intelligence,
        and information visualization. Peer-reviewed publications in network
        intelligence.
    }
}
\item \resemployer{IV Consulting, Inc.}{Tulsa, OK}
{Side venture between myself and a TU colleague as a custom software contractor,
working in database and web services.}
{
    \resjob{Partner/Developer}{Jul 2010}{Present}{
    Co-founder of the company as well as web and database developer in Python's
    Django framework. Developing two production systems for patient management
    and subject tracking for a psychiatric hospital and brain research
    institution. Responsible for back-end web development, project management,
    client relations, and documentation.
    }
}

\item \resemployer{Vidoop}{Tulsa, OK}
{Technology start-up company that produced a web-based multi-factor
authentication product and advertising platform.}
{
    \resjob{Security Research Intern}{May 2008}{Sep 2008}{
    Performed a vulnerability assessment on the user-facing portions of the
    company's authentication product. Developed proof-of-concept code for
    several attacks, including bypassing the product's CAPTCHA properties using
    computer vision. Delivered a comprehensive report and developed
    proof-of-concept mitigation strategies.
    }
    \resjob{Technical Writing Intern}{May 2007}{Mar 2009}{
    Served as a copy writer and editor for technical documentation,
    specifications, white papers, user documentation, and marketing materials.
    Developed, recorded, and narrated a series of educational videos for
    Vidoop's products as well as OpenID. Primary author on the corporate blog.
    Worked closely both with developers and business personnel. Staffed the
    company's exhibit at the IT Security World trade show.
    }
}
\end{itemize}


\resheading{Projects}

\begin{itemize}
\item
	\ressubheading{GSM Scale}{Tulsa, OK}{}{June 2010 - Present}
	\begin{itemize}
		\resitem{Developing a system for wirelessly collecting, recording, and analyzing patients' weights}
		\resitem{Working with Alexander Barclay (Laureate Institute for Brain Research), and Kevin Hall (National Institute of Diabetes and Digestive and Kidney Diseases)}
	\end{itemize}

\item
	\ressubheading{Cyber-physical Systems}{Tulsa, OK}{Institute for Information Security, TU}{Jan 2010 - Present}
	\begin{itemize}
		\resitem{Leading a formal methods research group for networked hybrid systems (i.e. systems with discrete and continuous components)}
		\resitem{Building a formal framework for modeling and analyzing networked process control systems}
	\end{itemize}

%\item
%	\ressubheading{Deployment Plan}{Tulsa, OK}{University of Tulsa}{Jan 2010 - May 2010}
%	\begin{itemize}
%		\resitem{Writing a comprehensive deployment plan for a generic enterprise computing system.}
%		\resitem{Included hardware and software deployment procedures and checklists, maintenance, as well as business IT policies (e.g. backup/restore, acceptable use, remote access, password, etc.)}
%	\end{itemize}

%\item
%	\ressubheading{Intrusion Detection System}{Tulsa, OK}{University of Tulsa}{Spring 2010}
%	\begin{itemize}
%		\resitem{Developing a Snort rule compatible network intrusion detection system in Java}
%		\resitem{Includes packet sniffing and parsing as well as generation, running directly on libpcap}
%	\end{itemize}

\item
	\ressubheading{SAND/DVNE}{Tulsa, OK}{Enterprise Security Group, TU}{May 2007 - Present}
	\begin{itemize}
		\resitem{Led a network monitoring research group}
		\resitem{Led the project's deployment at FAA Computer Security Incident Response Center}
		\resitem{Developing large-screen multi-touch network visualization system}
		\resitem{Presented with Cody Pollet at DEFCON 17 and as a poster at USENIX Security 2009}
	\end{itemize}
%\item
%	\ressubheading{Disastro}{Tulsa, OK}{University of Tulsa}{Jan 2009 - May 2009}
%	\begin{itemize}
%		\resitem{Functioned as technical lead and developer for a citizen-facing relief management system for disaster response}
%		\resitem{Integrated systems for voice phone (IVR), and web services for aggregation and dissemination of urgent relief information in disaster situations}
%	\end{itemize}
%\item
%	\ressubheading{Lunchman}{Tulsa, OK}{University of Tulsa}{Aug 2006 - May 2007}
%	\begin{itemize}
%		\resitem{Technical team member for a prototype web application for restaurant search and selection}
%		\resitem{Received runner-up award in the Donald W. Reynolds Governor's Cup business plan competition for 2007}
%	\end{itemize}
%\item
%	\ressubheading{NOVA}{Tulsa, OK}{Enterprise Security Group, TU}{Jan 2006 - May 2006}
%	\begin{itemize}
%		\resitem{Participated in development of a major network analysis project written in Java}
%		\resitem{Assisted deployment at FAA Computer Security Incident Responce Center}
%	\end{itemize}
\end{itemize}

\resheading{Academics}
    \resschool{Instructor}{}{}
	\ressubheading{Network Security}{Tulsa, OK}{University of Tulsa}{Spring 2010}
	\ressubheading{Secure System Administration}{Tulsa, OK}{University of Tulsa}{Spring 2010}
	\ressubheading{Risk Management for Information Systems}{Tulsa, OK}{University of Tulsa}{Spring 2010}
	\ressubheading{Computational Neuroscience}{Tulsa, OK}{University of Tulsa}{Fall 2009}
	\ressubheading{Information Systems Assurance}{Tulsa, OK}{University of Tulsa}{Fall 2009}
	\ressubheading{Machine Learning}{Tulsa, OK}{University of Tulsa}{Fall 2009}
	\ressubheading{Senior Software Projects}{Tulsa, OK}{University of Tulsa}{Fall 2008 - Spring 2009}
	\ressubheading{Compiler Construction}{Tulsa, OK}{University of Tulsa}{Fall 2008}
	\ressubheading{Operating Systems}{Tulsa, OK}{University of Tulsa}{Spring 2008}
	\ressubheading{Artificial Intelligence}{Tulsa, OK}{University of Tulsa}{Spring 2008}
	\ressubheading{Numerical Methods for IVP/BVPs}{Tulsa, OK}{University of Tulsa}{Spring 2008}
	\ressubheading{Computer Animation}{Tulsa, OK}{University of Tulsa}{Spring 2008}
	\ressubheading{Computer Networks}{Tulsa, OK}{University of Tulsa}{Fall 2007}
	\ressubheading{Enterprise Security Management}{Tulsa, OK}{University of Tulsa}{Spring 2007}
	\ressubheading{Computer Security}{Tulsa, OK}{University of Tulsa}{Spring 2006}
	\ressubheading{Computer Forensics}{Tulsa, OK}{University of Tulsa}{Spring 2006}
\resheading{Conferences}
\begin{center}
	\begin{tabular*}{6.5in}{m{5in}@{\extracolsep{\fill}}r}
		International Conference for High Performance Computing, Networking, Storage and Analysis 2008 (SC08) & Participant \\
		IT Security World Conference and Expo 2008 & Exhibitor \\
		12th TU Student Research Colloquium and 84th AAAS-SWARM Regional Meeting & Speaker, Session Chair \\
		DEFCON 16 & Participant (Human) \\
		Computer Security and Information Intelligence Research Workshop (CSIIRW) 2009 & Speaker \\
		The 2009 International Conference on Internet Computing (ICOMP `09) at WORLDCOMP `09 & Speaker \\
		DEFCON 17 & Speaker \\
		18th USENIX Security Symposium & Poster Presenter \\
		13th TU Student Research Colloquium & General Co-chair, Speaker \\
		Blackhat USA 2010 & Participant \\
		DEFCON 18 & Participant (Human) \\
		19th USENIX Security Symposium & Workshop Speaker \\
	\end{tabular*}
\end{center}

\resheading{Awards and Honors}
\begin{center}
	\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
		General Co-Chair, TU Student Research Colloquium & 2010 \\
		Chair, Computer Security Special Topic Symposium, TU Student Research Colloquium & 2010 \\
		Honorable Mention, Best Presentation, AAAS-SWARM 2009 & 2009 \\
%		Tulsa Undergraduate Research Challenge Participant & 2006-08\\
		Runner-Up, Donald W. Reynolds Governor's Cup Business Plan Competition & 2007\\
%		National Merit Scholar & 2005-2009\\
%		Oklahoma St. Regents for Higher Education Academic Scholar & 2005-2009\\
%		University of Tulsa Presidential Scholar & 2005-2009\\
%		Robert C. Byrd Academic Scholar & 2005-2009\\
	\end{tabular*}
\end{center}

\resheading{Publications and Presentations}
\begin{itemize}
\item
	\ressubheading{\emph{The Blunderdome: An Offensive Exercise for Building Network, Systems, and Web Security Awareness}\footnotemark[1]}{CSET 2010 at 19th USENIX Security Symposium}{P Gehres, N Singleton, G Louthan, and J Hale}{July 2010}
\item
	\ressubheading{\emph{Toward Sensitive Information Redaction in a Collaborative, Multilevel Security Environment}\footnotemark[1]}{WikiSym 2010}{P Gehres, N Singleton, G Louthan, and J Hale}{July 2010}
\item
	\ressubheading{\emph{Towards Formal Analysis of Cyber-Physical Systems}}{TU Colloquium}{G Louthan, N Singleton, M Papa, and J Hale}{March 2010}
\item
	\ressubheading{\emph{Large-scale Multitouch Interactive Network Visualization} (Poster)}{USENIX Security 18}{C Pollet, G Louthan and J Hale}{August 2009}
\item
	\ressubheading{\emph{SAND: An Architecture for Signature-based Automatic Network Protocol Detection} (Poster)}{USENIX Security 18}{G Louthan and J Hale}{August 2009}
\item
	\ressubheading{\emph{Hack Like the Movie Stars: A Big-Screen Multitouch Network Monitor}}{DEFCON 17}{G Louthan, C Pollet, and J Hale}{August 2009}
\item
	\ressubheading{\emph{Content-based Alternatives to Conventional Network Monitoring}\footnotemark[1]}{CSIIRW '09}{G Louthan, B Deetz, M Walker, and J Hale}{April 2009}
\item
	\ressubheading{\emph{Toward Robust and Extensible Network Protocol Identification}\footnotemark[1]}{ICOMP '09}{G Louthan, C McMillan, C Johnson, and J Hale}{July 2009}
\item
	\ressubheading{\emph{Communication without Boundaries: Breaching the Great Firewall of China}}{AAAS-SWARM '09}{G Louthan and J Hale}{March 2009}
\end{itemize}

\footnotetext[1]{Denotes a peer-reviewed publication}

\resheading{Skill set}
\begin{description}
\item[Programming Languages]
Java; Python; Clojure; Common Lisp; Basic; some Ruby, Perl and PHP
\item[Technologies]
TCP/IP; Computer networking; Shorewall/IPTables and general firewalling; Mathematica; \LaTeX; Network monitoring; Virtualization; some .NET
\item[Processes]
Risk management for information systems (NIST SP 800-30), including some familiarity with IT aspects of Sarbanes-Oxley risk assessment (PCAOB Auditing Standard 5); Information Security Management (ISO/IEC 17799:2005); Information Assurance Controls and Accreditation (NIST SP 800-53 and DoDI 8510.01); Incident response and computer forensics; General policy development; General familiarity with NIST 800 series
\item[Platforms]
Linux (especially Debian/Ubuntu); Windows 2000/XP/Vista/7 (Personal and Server versions); VMWare ESXi; OpenWrt/FreeWrt; Mac OS X
\item[Mathematics]
Numerical analysis; Finite difference methods; Finite element analysis; Real analysis; Discrete mathematics; Modern algebra; Finite state automata; Hybrid automata; Process calculi; Analysis of algorithms
\end{description}

%\resheading{Interests}
%
%\begin{description}
%\item[Academic] Computer security, Network monitoring and analysis, Network protocols, Free software, Distributed social networking
%\end{description}

\end{document}
